%----------------------------------------------------------------------------------------
%-------------------------------------- HOMEWORK 4b --------------------------------------
%----------------------------------------------------------------------------------------
\section{Assignment 4b \textit{-- Architecture Modeling with UML}}\label{Assignments::4b}
\textbf{Due:} February 24th, 2025 \\

\noindent
You are to design a software program that simulates a simple process of students going to school in the morning. You are given the following user story: John and Maria are two students at Stevens Institute of Technology, a local university. John gets to his classes by riding his bike and Maria gets to her class by putting on her shoes and walking to class. \\

\noindent
Model the above user story using the following modeling techniques:

\begin{enumerate}
    \item Create CRC cards depicting all the possible classes in the user story and extracting the CRC cards. For each CRC card make sure you describe the responsibilities and collaborations with the other classes (cards).
    \item Create a use case diagram, depicting the user story.
    \item Create an object diagram, depicting the exact scenario of the user story. Show all the associations.
    \item From the object diagram create a class diagram. Add as many association multiplicities and label any association ends as completely as you can. Make use of the following three association types: aggregation, composition, and generalization. This may require that you think of additional subclasses, in addition to the classes that the user story provided to you. You can use more than the three associations given above.

    Add at least one paragraph describing the thought process for each of the three diagrams. There is no right or wrong answer for this exercise. You will be graded on the completeness of your solution.
    \item Update your history table (\ref{Table::UpdateHistory}) and make sure you are generating a clean document, with a new chapter for this assignment. Up to 10 points are taken away for documents that are not "clean and organized."
\end{enumerate}