%----------------------------------------------------------------------------------------
%-------------------------------------- HOMEWORK 5 --------------------------------------
%----------------------------------------------------------------------------------------
\section{Assignment 5 \textit{-- Usability, Security, Safety and Energy Efficiency}}\label{Assignments::5}
\textbf{Due:} March 3rd, 2025 \\

\noindent
To your Overleaf Group Project, add a new chapter and title it: Usability, Security, Safety and Energy Efficiency.

\begin{enumerate}
    \item The oscilloscope is networked and shares data with labs that may be interested in remote monitoring of voltages.  The oscilloscope has a Wi-Fi and cellular connection.
    \item Write a concrete usability scenario for your Oscilloscope that specifies how long it takes you to adjust some aspect of the oscilloscope. Now consider another part of the user experience and create scenarios that test other aspects of the response measures from the general scenario table. (25 points)
    \item How might usability trade-off again security? How might it trade-off against performance? (25 points.)
    \item Pick two of the requirements of the Oscilloscope (i.e. voltage measurement, frequency measurement, peak-to-peak detection, something else) . Pick one appropriate response from the usability general scenario and an appropriate corresponding response measure. Use the response and response measure you chose, compare the scope's usability.  (25 points)
    \item What are the energy tradeoffs in your Oscilloscope between using Wi-Fi and the cellular network? (25 points)
    \item Please reference any outside sources with \verb|\cite{}| and add them to the bibliography file and please add at least 10x new \verb|\index{}| terms in this assignment.  You can add more, if you'd like.
\end{enumerate}