\chapter{Introduction \\
\small{\textit{-- ZKD, KRV, CL, \& ZZ}}
\index{Introduction} 
\index{Chapter!Introduction}
\label{Chapter::Introduction}}

\section{Team Roster}

\begin{longtable}{|p{6cm}|p{6cm}|}
%\centering
\caption{\TableName{Team Roster} \TableLabel{TeamRoster} \label{Table::TeamRoster}}\\
    
    \hline
    \textbf{Name} & \textbf{Email} \\
    \hline 
    \endhead

Zeel Kaushal Desai & \href{mailto:zdesai@stevens.edu}{zdesai@stevens.edu} \\ \hline

Krish Rakesh Vekaria & 
\href{mailto:kvekaria1@stevens.edu}{kvekaria1@stevens.edu} \\ \hline

Carson Lee & \href{mailto:clee27@stevens.edu}{clee27@stevens.edu} \\ \hline

Zhuo Zhang &
\href{mailto:zzhan114@stevens.edu}{zzhan114@stevens.edu} \\ \hline

Darian Muresan, Ph.D. & \href{mailto:dmuresan@stevens.edu}{dmuresan@stevens.edu} \\ \hline

\end{longtable}

\section{Team Members}
Below are short biographies for the four (4) team members in Group 3.

\subsection{Zeel Kaushal Desai}
Zeel Desai is a Master’s student in Software Engineering at Stevens Institute of Technology, with a Bachelor’s in Computer Science and Engineering, and a strong foundation in both web development and software engineering. As a motivated and detail-oriented Web Development Intern, I honed my skills in SQL, HTML, PHP, and JavaScript, gaining practical experience in both front-end and back-end web development. I am passionate about leveraging best practices in web development as well as software development to build scalable, efficient solutions while continuously expanding my technical expertise. Outside of academics, I enjoy reading, listening to music, and playing badminton, which help me stay motivated and balanced as I work toward my professional goals.

\subsection{Krish Rakesh Vekaria}
My name is Krish Vekaria, and I am currently a graduate student at Stevens Institute of Technology. My background is in software engineering and business analytics, with experience in machine learning and financial analytics. I have worked on various projects involving data science, stock market forecasting, and search engine development. My career goal is to secure a position at Google and eventually transition into a software management role.

\subsection{Carson Lee}
Carson Lee is a Software Engineering Major in the Accelerated Masters Program (AMP) at Stevens Institute of Technology. He graduated from Stevens last year with his Bachelors of Science in Computer Science. Born and raised in the small farm town of Hammonton, NJ, Carson enjoys spending time outdoors, hiking, camping, exploring new places, seeing musicals, and spending time with his friends.

Carson is well-versed in multiple programming languages with a majority being object-oriented languages such as C++ and Java. He is also currently employed by his university as a Teaching Assistant for CS-385: Computer Alogorithms where he teaches both principles of algorithms and C++.

\subsection{Zhuo Zhang}
My name is Zhuo Zhang. My background is in Computer Science and I graduated from University of Wisconsin-Superior in 2021. And I am currently a graduate student at Stevens Institute of Technology.